### 2014-06-21 docs/paper/paper.tex
software oscillator figure

\includegraphics[width=6in]{integrator-1d.eps} % FIXME software plot (for all figures)
% FIXME figure: larger axis and label font, make this consistent across all figures

@@

\begin{subfigure}[b]{\textwidth}
\centering
\lstset{language=Python}
\begin{lstlisting}[frame=single]
import nengo
import nengo.helpers
model = nengo.Model('Oscillator')
neurons = nengo.Ensemble(nengo.LIF(200), dimensions=2, 
  label='van der Pol Oscillator')
input = nengo.Node(output=nengo.helpers.piecewise(
  {0:[1,0], 0.1:[0,0], label='Initial condition')
tau = 0.1
freq = 5.0
input2output = nengo.Connection(input, neurons)
recurrent = nengo.Connection(neurons, neurons, 
  transform=[[1, -freq*tau],[freq*tau,1]], filter=tau)
input_probe = nengo.Probe(input, 'output')
neuron_probe = nengo.Probe(neurons, 'decoded_output', filter=0.005)
\end{lstlisting}
\caption{Source Code}
\label{lst:oscillator2d:code}
\end{subfigure}

@@

\begin{figure}
\centering
\includegraphics[width=6in]{oscillator-2d.eps}

\caption[Simulation of a 2D neural oscillator.]
{Hardware output from the simulation of a two-dimensional population representing a neural oscillator.}
\label{fig:oscillator2d}
\end{figure}

>>>>

\includegraphics[width=6in]{integrator-1d.eps} % FIXME software plot
% FIXME figure: larger axis and label font, make this consistent across all figures

@@

\begin{subfigure}[a]{\textwidth}
\centering
\lstset{language=Python}
\begin{lstlisting}[frame=single]
import nengo
import nengo.helpers
model = nengo.Model('Oscillator')
neurons = nengo.Ensemble(nengo.LIF(200), dimensions=2, 
  label='van der Pol Oscillator')
input = nengo.Node(output=nengo.helpers.piecewise(
  {0:[1,0], 0.1:[0,0], label='Initial condition')
tau = 0.1
freq = 5.0
input2output = nengo.Connection(input, neurons)
recurrent = nengo.Connection(neurons, neurons, 
  transform=[[1, -freq*tau],[freq*tau,1]], filter=tau)
input_probe = nengo.Probe(input, 'output')
neuron_probe = nengo.Probe(neurons, 'decoded_output', filter=0.005)
\end{lstlisting}
\caption{Source Code}
\label{lst:oscillator2d:code}
\end{subfigure}

@@

\begin{figure}[h!]
\centering

\begin{subfigure}[a]{0.4\textwidth}
\centering
\includegraphics[width=4in]{oscillator-2d.eps}
\caption{Hardware simulation}
\label{fig:oscillator2d:hw}
\end{subfigure}

\begin{subfigure}[b]{0.4\textwidth}
\centering
\includegraphics[width=4in]{oscillator-2d-sw.eps}
\caption{Software simulation}
\label{fig:oscillator2d:sw}
\end{subfigure}

\caption[Simulation of a 2D neural oscillator in hardware and software.]
{Hardware (\ref{fig:oscillator2d:hw}) and software (\ref{fig:oscillator2d:sw}) output from the simulation of a two-dimensional population representing a neural oscillator.}
\label{fig:oscillator2d}
\end{figure}
